% ============================================================
% MASTER RESUME — your single source of truth.
%
% *** FICTIONAL TEST DATA ***
% This content (Jordan Ruiz) is a made-up persona used only to test
% the cross-tool-portability skills on the `development` branch.
% It is NOT a real candidate. Do not commit your real details over
% this file on a pushed/public branch — fill in your real resume
% locally and keep it uncommitted (or gitignored) instead.
%
% Put EVERYTHING here: all jobs, all projects, all skills, all
% numbers. It can be several pages long — it is NEVER sent
% anywhere. The tailor skill selects from this file to build
% one-page tailored resumes per job.
%
% DESIGN NOTES (keep these — they make it ATS-safe AND clean):
%  - Single column, standard fonts, no tables/graphics/icons.
%  - Contact info in the body (not in a header/footer).
%  - Consistent section rule via titlesec (never clamps text).
%  - " | " separators, no em dashes.
% ============================================================
\documentclass[11pt]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}
\usepackage{titlesec}
\pagestyle{empty}

% Consistent section style: title, small gap, full-width rule.
\titleformat{\section}
  {\large\bfseries}{}{0pt}{}[\vspace{2pt}\hrule]
\titlespacing*{\section}{0pt}{8pt}{4pt}

% Job/entry header: "Title | Organisation, Location            Dates"
\newcommand{\job}[4]{% title, org, location(with leading ", " or empty), dates
  \vspace{4pt}{\bfseries #1} | #2#3 \hfill #4\par}

\setlist[itemize]{leftmargin=15pt, itemsep=1pt, topsep=2pt, parsep=0pt}

\begin{document}

% ---------- CONTACT ----------
\begin{center}
{\LARGE\bfseries Jordan Ruiz}\\[3pt]
Austin, TX, USA $\vert$ jordan.ruiz.test@example.com $\vert$ +1 512 555 0134\\[1pt]
\href{https://linkedin.com/in/jordanruiz-test}{linkedin.com/in/jordanruiz-test} $\vert$
\href{https://github.com/jordanruiz-test}{github.com/jordanruiz-test} $\vert$
\href{https://jordanruiz.example.com}{jordanruiz.example.com}
\end{center}

% ---------- SUMMARY ----------
\section{Summary}
Backend-leaning software engineer with 5 years of experience building and
scaling Python and Node.js services on AWS. Strongest in API design, event
pipelines, and deployment automation. Cut failed-deploy recovery time by
60\% by building automated rollback tooling.

% ---------- SKILLS ----------
\section{Skills}
\textbf{Languages:} Python, TypeScript/JavaScript, SQL, Go\\
\textbf{Backend \& Cloud:} FastAPI, Django, Node.js/Express, AWS (Lambda, ECS, RDS), Docker, Kubernetes\\
\textbf{Data \& Tools:} PostgreSQL, Redis, Kafka, Airflow, Terraform, GitHub Actions\\
\textbf{Spoken:} English (native), Spanish (conversational)

% ---------- WORK EXPERIENCE ----------
\section{Work Experience}

\job{Backend Engineer}{Northlake Systems}{, Austin, TX}{Jun 2022 - Present}
\begin{itemize}
  \item Redesigned the order-processing API from a monolith into 6 microservices
        using FastAPI and Docker, cutting average response time from 480ms to 140ms.
  \item Built a Kafka-based event pipeline processing 2.3M events per day,
        replacing a nightly batch job and reducing data staleness from 24 hours
        to under 5 minutes.
  \item Automated deployment rollback tooling with GitHub Actions and Terraform,
        cutting failed-deploy recovery time by 60\%.
  \item Migrated the primary PostgreSQL database to a read-replica architecture,
        cutting peak query latency by 35\% during traffic spikes.
  \item Mentored 3 junior engineers through a structured onboarding program,
        shortening ramp-up time from 8 weeks to 5.
  \item Introduced contract testing between 4 internal services using Pact,
        reducing integration bugs caught in staging by 45\%.
  \item Wrote internal runbooks and documentation that cut on-call escalations
        by 30\%.
\end{itemize}

\job{Software Engineer}{BrightPath Analytics}{, Remote}{Mar 2020 - May 2022}
\begin{itemize}
  \item Built a customer-facing analytics dashboard in React and Node.js used
        by over 1,200 monthly active clients.
  \item Developed ETL pipelines in Python and Airflow ingesting data from
        15+ third-party APIs, processing 500,000+ records daily.
  \item Implemented role-based access control across 3 internal applications,
        closing a security gap flagged in a client audit.
  \item Optimized a reporting SQL query from 12 seconds to 900ms by adding
        targeted indexes and rewriting joins.
  \item Shipped a self-serve data export feature with the product team,
        reducing support tickets related to data requests by 25\%.
  \item Wrote unit and integration tests that raised backend test coverage
        from 40\% to 78\%.
\end{itemize}

% ---------- PROJECTS ----------
% Personal, freelance, open-source, or capstone projects all belong here.
\section{Projects}

\job{shipwatch (open-source CLI)}{Python, Click, GitHub Actions}{}{2023}
\begin{itemize}
  \item Built and published a CLI tool that monitors GitHub Actions workflow
        health across multiple repos, reaching 300+ GitHub stars.
  \item Added Slack alerting integration, adopted by 2 other engineering teams
        outside the original project.
\end{itemize}

\job{Kubernetes autoscaling demo (bootcamp capstone)}{Kubernetes, Terraform, AWS}{}{2022}
\begin{itemize}
  \item Built a demo cluster with horizontal pod autoscaling triggered by
        custom Prometheus metrics, presented to a panel of 4 industry mentors.
\end{itemize}

\job{Personal finance tracker}{TypeScript, Next.js, PostgreSQL}{}{2021}
\begin{itemize}
  \item Built a self-hosted budgeting app with automatic bank-statement CSV
        parsing and category tagging.
  \item Used by a group of 20 beta users; iterated across 3 releases based on
        their feedback.
\end{itemize}

% ---------- EDUCATION ----------
% Degrees AND bootcamps/academies/training programmes go here.
\section{Education}
\job{B.S. Computer Science}{University of Texas at Austin}{}{2016 - 2020}
GPA 3.6/4.0. Relevant coursework: Distributed Systems, Databases, Algorithms.

\job{Cloud Infrastructure Bootcamp}{CloudForge Academy}{}{2022}
8-week intensive programme in AWS and Kubernetes infrastructure; team
capstone project (see Projects).

% ---------- CERTIFICATIONS ----------
\section{Certifications}
\begin{itemize}
  \item AWS Certified Solutions Architect - Associate — Amazon Web Services, 2023
  \item Terraform Associate — HashiCorp, 2022
\end{itemize}

\end{document}
